---
title: "Bicycle infrastructure, Atlanta; August, 2018"
author: "Michael D Garber"
date: "`r Sys.Date()`"
output:
  html_document:
#    toc: true
#    toc_float: true
    number_sections: false
---

Update June 5th, 2023. Removing pop-ups for speed.
Update Jul 22, 2023: I'm updating the other file as well, so these should be identical.


# Map of bicycle infrastructure in Atlanta

Bicycle infrastructure in Atlanta within a 5.5-mile radius around Ponce de Leon Ave NE and Monroe Dr NE as of August of 2018.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(sf)
library(here)
library(mapview)
library(RColorBrewer)
library(leaflet)
library(leaflet.extras) #for popping out full screen
#Note see diss/scripts/aim3-figures.R
setwd(here("data-processed"))
load("edge_mo_infra_study_mo_23_geo.RData")#from aim-3-figures.R
load("mp_sf_5halfmi.RData")
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(RColorBrewer)
library(shades)
greens_6_middle3 = RColorBrewer::brewer.pal(n=6, name  = "Greens")[5:3]  
greens_4 = RColorBrewer::brewer.pal(n=4, name  = "Greens") 
blues_6_top4  = RColorBrewer::brewer.pal(n=6, name  = "Blues")[6:3] 
oranges_6_top4  = RColorBrewer::brewer.pal(n=6, name  = "Oranges")[6:3] 
purples_6_top4  = RColorBrewer::brewer.pal(n=6, name  = "Purples")[6:3] 

infra_custom_pal = c(
  "black",
  brewer.pal(n=3, "Greens")[3],
  brewer.pal(n=3, "Blues")[3],
  brewer.pal(n=3, "Oranges")[3],
  brewer.pal(n=3, "Purples")[3]
)

mv_mp_sf_5halfmi = mp_sf_5halfmi %>% 
  mapview(
    alpha.regions = 0,
    color = "grey40", col.regions = "grey40",
        popup=FALSE,#might reduce size
        layer.name = "Study area")

mv_infra_study_mo_23_infra_custom_pal = edge_mo_infra_study_mo_23_geo %>% 
  #remove some extraneous vars I don't want included in an interactive map
  dplyr::select(
    -starts_with("infra_exclude")) %>% 
  mapview(
    zcol =  "infra_6cat_long_legend_nodirt",  
    color = infra_custom_pal,
    #what about turbo?
#   color=turbo(n=n_distinct(edge_mo_infra_study_mo_23_geo$infra_6cat_long)),
    layer.name = "Infrastructure" ,
    lwd=3,
    popup=FALSE,#might reduce size
    alpha=0.9
  )  

mv_infra_custom_pal_both=mv_infra_study_mo_23_infra_custom_pal+ 
  mv_mp_sf_5halfmi
#remove map junk
# mv_infra_custom_pal_both_no_junk=mv_infra_custom_pal_both %>% 
#   mapview::removeMapJunk(
#     junk = c(
#       "layersControl",
#       "zoomControl"
#     ))


mv_infra_custom_pal_both

#Having issues. Try without the ability to pop out full screen.
#so that it can be popped out full screen
# mv_infra_custom_pal_both@map %>% 
#   leaflet.extras::addFullscreenControl()
```

# Map of bicycle infrastructure in Atlanta by roadway type

Bicycle infrastructure in Atlanta within a 5.5-mile radius around Ponce de Leon Ave NE and Monroe Dr NE as of August of 2018, stratified by roadway type. A map of roadway type is here: <https://michaeldgarber.github.io/diss/atl-osm-roadway-type>
```{r, echo=FALSE, warning=FALSE, message=FALSE}
#This is long. Make sure it's consistent with 
#~diss/scripts/aim3-figures.R

# Map: infra by highway-------
#Revising this using edge_mo_infra_study_mo_23_geo
#Also use hwy_5 instead of hwy_5
#instead
## define study area-----------
setwd(here("data-processed"))
#lookup_hwy_5 is created in 9_aim3_working_sample.R
load("lookup_hwy_5.RData")

mv_mp_sf_5halfmi = mp_sf_5halfmi %>% 
  mapview(
    alpha.regions = 0,
              popup=FALSE,#might reduce size
    color = "grey40", col.regions = "grey40",
        layer.name = "Study area")

lwd_value = 5
## infra by highway lane_p------------
greens_6_middle3 = RColorBrewer::brewer.pal(n=6, name  = "Greens")[5:3]  
greens_4 = RColorBrewer::brewer.pal(n=4, name  = "Greens") 
mapview_lane_p_by_highway = edge_mo_infra_study_mo_23_geo %>% 
  filter(infra_6cat_long_legend_nodirt=="2-Lane-Protected") %>% 
  left_join(lookup_hwy_5,by="edge_id") %>% 
  mapview(zcol = "hwy_5",
          color  = greens_6_middle3,
          layer.name = "Protected bike lane by roadway type" ,
          lwd=lwd_value,
          popup=FALSE,#might reduce size
          alpha=1)

## infra by highway lane_b--------
blues_6_top4  = RColorBrewer::brewer.pal(n=6, name  = "Blues")[6:3] 
mapview_lane_b_by_highway = edge_mo_infra_study_mo_23_geo %>% 
  filter(infra_6cat_long_legend_nodirt=="3-Lane-Buffered") %>% 
  left_join(lookup_hwy_5,by="edge_id") %>%  
  filter(is.na(hwy_5)==FALSE) %>% 
  mapview(zcol = "hwy_5",
          color  = blues_6_top4,
          layer.name = "Buffered bike lane by roadway type" ,
          lwd=lwd_value,
                    popup=FALSE,#might reduce size
          alpha=1)

## infra by highway lane_c----------
oranges_6_top4  = RColorBrewer::brewer.pal(n=6, name  = "Oranges")[6:3] 
mapview_lane_c_by_highway = edge_mo_infra_study_mo_23_geo %>% 
  filter(infra_6cat_long_legend_nodirt=="4-Lane-Conventional") %>% 
  left_join(lookup_hwy_5,by="edge_id") %>%  
  filter(is.na(hwy_5)==FALSE) %>% 
  mapview(zcol = "hwy_5",
          color  = oranges_6_top4,
          layer.name = "Conventional bike lane by roadway type" ,
          lwd=lwd_value,
                    popup=FALSE,#might reduce size
          alpha=1)


## infra by highway sharrow-------------
purples_6_top4  = RColorBrewer::brewer.pal(n=6, name  = "Purples")[6:3] 

mapview_sharrow_by_highway = edge_mo_infra_study_mo_23_geo %>% 
  filter(infra_6cat_long_legend_nodirt=="5-Sharrow") %>% 
  left_join(lookup_hwy_5,by="edge_id") %>%  
  filter(is.na(hwy_5)==FALSE) %>% 
  mapview(zcol = "hwy_5",
          color  = purples_6_top4,
          layer.name = "Sharrow by roadway type" ,
          lwd=lwd_value,
                    popup=FALSE,#might reduce size
          alpha=1)

## infra by off-street paved trail-------------
#al_grey = "#969696"
mapview_trail_p = edge_mo_infra_study_mo_23_geo %>% 
  filter(infra_6cat_long_legend_nodirt=="1-Trail-Paved") %>% 
  left_join(lookup_hwy_5,by="edge_id") %>%  
  mutate(
    #make a legend dummy
    legend_dummy = " "
  ) %>% 
  mapview( 
    color = "black" ,
              popup=FALSE,#might reduce size
    layer.name = "Off-street paved trails" ,
    lwd=3, #note less line width
    alpha=1)



## infra by highway mapviews-------------

mv_infra_by_hwy_all=mv_mp_sf_5halfmi+
  mapview_trail_p+
  mapview_lane_p_by_highway +
  mapview_lane_b_by_highway +
  mapview_lane_c_by_highway +
  mapview_sharrow_by_highway

#remove junk
# mv_infra_by_hwy_all_no_junk=mv_infra_by_hwy_all %>% 
#   mapview::removeMapJunk(
#     junk = c(
#       "layersControl",
#       "zoomControl"
#     ))

mv_infra_by_hwy_all

#so that it can be popped out full screen
# mv_infra_by_hwy_all@map %>% 
#   leaflet.extras::addFullscreenControl()
```
