---
title: "Read bicycle infrastructure data and convert to other formats: demo"
author: "Michael D. Garber"
date: "`r Sys.Date()`"
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    toc_depth: 4
---

This is a demo showing how the bicycle infrastructure data that I may post publicly may be read into R and converted into other formats, such as shapefiles compatible with Esri software and CSVs.

# Load R packages

I use the [here](https://github.com/jennybc/here_here) package to manage relative folder paths. On my computer, the data are in a folder called "data-to-share", which is in a folder called, "data-processed", which is one level beneath the folder containing my RStudio project file. I use the [sf](https://r-spatial.github.io/sf/) package to manage the vector spatial data.

```{r, echo=T, warning=FALSE, message=FALSE}
library(here)
library(sf)
library(tidyverse)
library(tmap) #static maps
library(mapview) #interactive maps
library(knitr)#to use kable
```

# Read and explore data

## Segments

Load spatial data

```{r, echo=T, warning=FALSE, message=FALSE}
setwd(here("data-processed","data-to-share"))
load("lookup_edge_geo.RData")
```

How many observations in the spatial data?

```{r}
nrow(lookup_edge_geo)
```

Map the segments

```{r}
lookup_edge_geo %>% 
  tm_shape()+
  tm_lines()
```

Load aspatial data

```{r, echo=T, warning=FALSE, message=FALSE}
setwd(here("data-processed","data-to-share"))
load("edge_month_share.RData")
```

How many observations are in the aspatial data?

```{r}
nrow(edge_month_share)
```

How many unique edge_ids?

```{r}
n_distinct(edge_month_share$edge_id)
```

How many months?

```{r}
n_distinct(edge_month_share$study_month)
```

How many miles of bicycle infrastructure during the last study month?

```{r}
edge_month_share %>% 
  filter(study_month==24) %>% 
  group_by(infra_6cat_long_legend_nodirt) %>%
  summarise(length_mi=sum(length_mi,na.rm=TRUE)) %>% 
  kable()
```

The bicycle infrastructure data in August of 2018 are mapped here:

<https://michaeldgarber.github.io/diss/atl-bike-infra-201808>

## Intersections
Load spatial data on intersections
```{r, echo=T, warning=FALSE, message=FALSE}
setwd(here("data-processed","data-to-share"))
load("lookup_inters_geo.RData")
names(lookup_inters_geo)
```

How many intersections?
```{r}
nrow(lookup_inters_geo)
```

Load the one-to-many look-up table between intersections and edges
```{r, echo=T, warning=FALSE, message=FALSE}
setwd(here("data-processed","data-to-share"))
load("lookup_inters_edge_nogeo.RData")
```

How many edges per intersection?
```{r}
lookup_inters_edge_nogeo %>% 
  group_by(inters_id) %>% 
  summarise(n_edges=n()) %>% 
  ungroup() %>% 
  mutate(dummy=1) %>% 
  group_by(dummy) %>% 
  summarise(
    n_edges_per_inters_mean=mean(n_edges,na.rm=T),
    n_edges_per_inters_med=median(n_edges,na.rm=T),
    n_edges_per_inters_min=min(n_edges,na.rm=T),
    n_edges_per_inters_max=max(n_edges,na.rm=T)
    ) %>% 
  pivot_longer(-contains("dummy")) %>% 
  dplyr::select(-contains("dummy")) %>% 
  kable()
```

How many observations in the aspatial data?

# Convert to other formats 
## Convert intersections to points

It may be desirable to convert intersections to points, as the file size is smaller. That can be done using `st_centroid()` from the sf package.
```{r, echo=F, warning=FALSE, message=FALSE}
setwd(here("data-processed","data-to-share"))
load("lookup_inters_point_geo.RData")
```

```{r, eval=F, warning=FALSE, message=FALSE}
lookup_inters_point_geo=lookup_inters_geo %>% 
  st_centroid()
```

Map the intersections represented as points:
```{r, eval=T, warning=FALSE, message=FALSE}
lookup_inters_point_geo %>% 
  tm_shape()+
  tm_dots()
```


## Convert spatial data to shapefiles

Convert the segment-level vector data data to shapefiles:
```{r, eval=F, echo=T, warning=FALSE, message=FALSE}
setwd(here("data-processed","data-to-share","shapefiles-edge"))
st_write(lookup_edge_geo, 
         dsn = "lookup_edge_geo.shp",
         append=FALSE,#overwrite
         layer = "lookup_edge_geo.shp", driver = "ESRI Shapefile")
```

Convert the intersection-level vector data to shapefiles:
```{r, eval=F, echo=T, warning=FALSE, message=FALSE}
setwd(here("data-processed","data-to-share","shapefiles-intersection"))
st_write(lookup_inters_geo, 
         dsn = "lookup_inters_geo.shp",
         append=FALSE,#overwrite
         layer = "lookup_inters_geo.shp", driver = "ESRI Shapefile")
```

## Convert aspatial data to CSVs
```{r, eval=F, echo=T, warning=FALSE, message=FALSE}
setwd(here("data-processed","data-to-share","csv"))
write_csv(edge_month_share,file="edge_month_share.csv")
```

Warning: the aspatial data contains 1,583,952 observations so may not load in Excel, as Excel 2010 is limited to [1,048,576 rows](https://support.microsoft.com/en-au/office/excel-specifications-and-limits-1672b34d-7043-467e-8e27-269d656771c3).
