---
title: "Demo code to read bicycle infrastructure data and convert to other formats"
author: "Michael D. Garber"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: false
---

This is a demo showing how the bicycle infrastructure data posted in this repository (<https://doi.org/10.7910/DVN/JE9OWB>) may be read into R and converted into other formats, such as shapefiles compatible with Esri software and CSVs.

# Load R packages

I use the [here](https://github.com/jennybc/here_here) package to manage relative folder paths. On my computer, the data are in a folder called "data-to-share", which is in a folder called, "data-processed", which is one level beneath the folder containing my RStudio project file. I use the [sf](https://r-spatial.github.io/sf/) package to manage the vector spatial data.

```{r, echo=T, warning=FALSE, message=FALSE}
library(here)
library(sf)
library(tidyverse)
library(tmap) #static maps
library(mapview) #interactive maps
```

# Read and explore data

## Segments

Load spatial data

```{r, echo=T, warning=FALSE, message=FALSE}
setwd(here("data-processed","data-to-share"))
load("lookup_edge_geo.RData")

```

How many observations in the spatial data?

```{r}
nrow(lookup_edge_geo)
```

Map the segments

```{r}
lookup_edge_geo %>% 
  tm_shape()+
  tm_lines()
```

Load aspatial data with

How many observations in the aspatial data?

Map the infrastructure during the last month under observation

## Intersections

How many observations in the spatial data?

How many observations in the aspatial data?

# Convert intersections to points

It may be desirable to convert intersections to points, as the file size is smaller. That can be done using `st_centroid()` from the sf package.

# Convert spatial data to shapefiles

Convert the segment-level data vector data to shapefiles:

Convert the intersection-level vector data to shapefiles:

# Convert aspatial data to CSVs

Warning: the aspatial data contains x observations, and Excel 2010 is limited to [1,048,576 rows](https://support.microsoft.com/en-au/office/excel-specifications-and-limits-1672b34d-7043-467e-8e27-269d656771c3).
